Continuous developmental change can explain discontinuities in word learning

### 2019-02-02 cogsci/cogsci.Rmd
final version cogsci

author-information: > 
    \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Sophie Regan} \\ \texttt{sregan20@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data. A word is represented with a distribution over the perceptual space (indicated in red or green). When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score. The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel)."}

@@

One limitation of this work is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-18 month-old). We selected this age group based on two measurement issues. First, model fitting requires several, reliably-measured data points. In our case, data collection involved presenting participants with several trials across four conditions in a between-subject design. It would have been challenging to obtain these measures with infants. Second, experiments with infants on this topic have often used habituation methods [but cf. @yoshida2009], which require additional linking assumptions. Indeed, it is not clear how data from these methods would directly compare to data collected using more typical methods in older children and adults.
<!--While an important conclusion of this paper is that the same process may apply to different developmental stages, it would be interesting to experimentally verify the generality of this conclusion in the context of early language acquisition. A challenge to this next step would be to construct a computational framework which would compare performance across heterogeneous testing methods (e.g., looking time vs. forced-choice). -->

@@

<!--
\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}

# Acknowledgements

This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.

-->
# References

>>>>

author-information: >

    \author{{\large \bf Anonymous CogSci submission} \\  \\ \\ }

@@

```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data. A word is represented with a distribution over the perceptual space (indicated in red or blue). When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score. The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel)."}

@@

One limitation of this work is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-18 month-old). We selected this older age group to optimize the number and precision of the experimental measures (both are crucial to model fitting). Data collection involved presenting participants with several trials across four conditions in a between-subject design. It would have been challenging to obtain such measures with infants. <!--Second, experiments with infants on this topic have often used habituation methods [but cf. @yoshida2009], which require additional linking assumptions. Indeed, it is not clear how data from these methods would directly compare to data collected using more typical methods in older children and adults.
-->
<!--While an important conclusion of this paper is that the same process may apply to different developmental stages, it would be interesting to experimentally verify the generality of this conclusion in the context of early language acquisition. A challenge to this next step would be to construct a computational framework which would compare performance across heterogeneous testing methods (e.g., looking time vs. forced-choice). -->

@@

\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}} \vspace{1em}

<!--
# Acknowledgements

This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.
-->

# References

### 2019-02-02 cogsci/cogsci.tex
final version cogsci

\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Sophie Regan} \\ \texttt{sregan20@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

\caption{\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data. A word is represented with a distribution over the perceptual space (indicated in red or green). When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score. The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel).}\label{fig:illus}
\end{figure}
\end{CodeChunk}

@@

One limitation of this work is that the model was fit to data from
children at a relatively older age (4-5 years old) than what is
typically studied in the literature (14-18 month-old). We selected this
age group based on two measurement issues. First, model fitting requires
several, reliably-measured data points. In our case, data collection
involved presenting participants with several trials across four
conditions in a between-subject design. It would have been challenging
to obtain these measures with infants. Second, experiments with infants
on this topic have often used habituation methods (but cf. Yoshida et
al., 2009), which require additional linking assumptions. Indeed, it is
not clear how data from these methods would directly compare to data
collected using more typical methods in older children and adults.

@@

>>>>

\author{{\large \bf Anonymous CogSci submission} \\  \\ \\ }

@@

\caption{\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data. A word is represented with a distribution over the perceptual space (indicated in red or blue). When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score. The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel).}\label{fig:illus}
\end{figure}
\end{CodeChunk}

@@

One limitation of this work is that the model was fit to data from
children at a relatively older age (4-5 years old) than what is
typically studied in the literature (14-18 month-old). We selected this
older age group to optimize the number and precision of the experimental
measures (both are crucial to model fitting). Data collection involved
presenting participants with several trials across four conditions in a
between-subject design. It would have been challenging to obtain such
measures with infants.

@@

\vspace{1em}

\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}}
\vspace{1em}
